---
title: "Google Analytics"
subtitle: "2021 Wrapped Up"
author: "Kerim Kiliç"
date: "26/12/2021"
output: 
  beamer_presentation:
    theme: "AnnArbor"
    colortheme: "beaver"
    fonttheme: "structurebold"
    slide_level: 1
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

install.packages("RGoogleAnalytics")
install.packages("tidyverse")
install.packages("scales")
install.packages("gridExtra")

library(RGoogleAnalytics)
library(tidyverse)
library(scales)
library(gridExtra)
```

```{r, message=FALSE, warning=FALSE}
get_data <- function(start.date,end.date,dimensions,metrics)
{
  query <- Init(start.date = start.date,
                end.date = end.date,
                dimensions = dimensions,
                metrics = metrics,
                max.results = 10000,
                sort = paste("-",dimensions,sep=""),
                table.id = "ga:<table.id>"
                )
  ga.query <- QueryBuilder(query)
  return(GetReportData(ga.query, token))
}
```


```{r, message=FALSE, warning=FALSE}
token <- Auth(client.id="<ga:client.id>",
              client.secret="<ga:client.secret>")
ValidateToken(token)
```

# Geographic data

```{r,message=FALSE,warning=FALSE,out.height="90%"}
df2 <- get_data("2021-01-01",
               "2021-12-25",
               "ga:year,ga:country",
               "ga:sessions,ga:pageviews,ga:users,ga:avgSessionDuration"
               )

df3 <- df2[with(df2,order(-sessions)),]%>%slice(1:5)
p1 <- ggplot(df3, aes(x = reorder(country, sessions), y=sessions)) + 
  geom_bar(position="dodge",stat="identity", alpha=.9, width=.5,fill="#a40000") +
  scale_y_continuous(limits = c(0,300), breaks=seq(0,300,50)) + 
  labs(x = "Country",y="Sessions", title ="Top 5 countries") + 
  coord_flip() +
  theme(
    axis.line.x = element_line(colour = "grey50"),
    axis.line.y = element_line(colour = "grey50"),
  ) +
  theme_light()

df5 <- get_data("2021-01-01",
               "2021-12-25",
               "ga:year,ga:city",
               "ga:sessions,ga:pageviews,ga:users,ga:avgSessionDuration"
               )
df6 <- df5[with(df5,order(-sessions)),]%>%filter(city != "(not set)")%>%slice(1:5)

p2 <- ggplot(df6, aes(x = reorder(city, sessions), y=sessions)) + 
  geom_bar(position="dodge",stat="identity", alpha=.9, width=.5,fill="#a40000") +
  scale_y_continuous(limits = c(0,125), breaks=seq(0,125,25)) + 
  labs(x = "City",y="Sessions", title ="Top 5 cities") + 
  coord_flip() +
  theme(
    axis.line.x = element_line(colour = "grey50"),
    axis.line.y = element_line(colour = "grey50"),
  ) +
  theme_light()

grid.arrange(p1,p2,ncol=2)
```

# Channels

```{r,message=FALSE,warning=FALSE,out.height="90%"}
df4 <- get_data("2021-01-01",
               "2021-12-25",
               "ga:year,ga:channelGrouping",
               "ga:sessions,ga:pageviews,ga:users,ga:avgSessionDuration"
               )

ggplot(df4, aes(x = reorder(channelGrouping, sessions), y=sessions)) + 
  geom_bar(position="dodge",stat="identity", alpha=.9, width=.5,fill="#a40000") +
  scale_y_continuous(limits = c(0,300), breaks=seq(0,300,50)) + 
  labs(x = "Channel type",y="Sessions", title ="Sessions per channel type") + 
  coord_flip() +
  theme(
    axis.line.x = element_line(colour = "grey50"),
    axis.line.y = element_line(colour = "grey50"),
  ) +
  theme_light()
```


# Pageviews over time

```{r,out.height="90%"}
df1 <- get_data("2021-01-01",
               "2021-12-25",
               "ga:month",
               "ga:sessions,ga:pageviews,ga:users,ga:avgSessionDuration,ga:pageviewsPerSession")

df1$month <- as.Date(paste(df1$month,"-01-2021",sep=""),"%m-%d-%y")
df1 <- df1%>%filter(sessions!=0)

ggplot(df1, aes(x = month, y=pageviews)) +
  geom_line(size=.75,color="#a40000") + 
  labs(x = "Month",y="Pageviews",title="Page views over time in 2021") + 
  scale_y_continuous(limits = c(0,600), breaks=seq(0,600,100)) + 
  scale_x_date(labels = date_format("%b"), date_minor_breaks = "month",date_breaks = "1 month") +
  geom_point(size=2,color="#a40000") +
  theme(
    axis.line.x = element_line(colour = "grey50"),
    axis.line.y = element_line(colour = "grey50"),
  ) +
  theme_light()
```

# 2021 Website statistics wrapped up

```{r,message=FALSE, warning=FALSE}
# Pageviews and users
total_pageviews <- sum(df1$pageviews)
total_users <- sum(df1$users)
# Average session duration
seconds <- round(mean(df1$avgSessionDuration)%%60)
time <- mean(df1$avgSessionDuration)-mean(df1$avgSessionDuration)%%60
minutes <- time/60
# Total countries and cities
total_countries <- nrow(df2)
total_cities <- nrow(df5)-1
# Average pages per session
avg_pages_per_session <- round(mean(df1$pageviewsPerSession),2)
```

- **`r total_pageviews`** total page views

- **`r total_users`** total users
  - From **`r total_countries`** countries and **`r total_cities`** different cities.

- Average session duration of **`r minutes`** minutes and **`r seconds`** seconds.

- Average number of pages per session of **`r avg_pages_per_session`**.

- Created using **[R](https://www.r-project.org/)** and the **[Google Analytics API](https://developers.google.com/analytics)**.

- **[Click here](https://github.com/kerim-kilic/google-analytics-data)** to download to code from my GitHub.
